Design and Implementation of Stable High Power Optical Lattices for Quantum Gas Microscopy

### 2017-01-29 LatticeOptics/latticeOpticsV2.tex
text change

\section{Photodiodes}
FIGURE: Transimpedance amplifier, with our parameters
\begin{itemize}
	\item Transimpedance amplifier - typical parameters
	\item design criteria, part numbers, typical voltage levels
	\item cutting off windows
	\item thermal stuff (inGas)
	\item lens or no
	\item using photodiodes for looking at these thing
\end{itemize}

@@

Passive stability, while critical, has been found to be insufficient to ensure smoothe operation over many hours. Changes in weather conditions, load on the water-cooling systems and other external effects can lead to a slow drift in the pointing of the laser beams. 
To prevent external influences from contaminating large data sets, we have implemented an independent monitoring system to verify appropriate pointing of both lattice laser beams.
This system is based on picking off a small portion of the beam shortly before it reaches the atomic system and imaging it onto a camera in the same plane as the atoms. 
While the position of the atoms is dictated by the potential generated from the ingoing and retro-reflected laser beams and the monitoring camera only observes the position of the ingoing beam.
In order to verify that the monitor camera \dots
purposeful misalignment of the ingoing beam shows a clear correlation between the monitor camera signal and the

Typical operation of the experiment involves repeated realizations of the ultracold atomic system, with a cycle time of 10s of seconds, with a lattice duty cycle of about 10\%.

>>>>

\section{Photodiodes}
Fast, low-noise photodiodes are required both to provide the monitoring arm of the feedback loop and to characterize the RIN of the system.
An ideal device would have a bandwidth up to approximately 3 MHz, with a noise floor below approximately -150 dBc over that range.
To approach these specifications, we use a custom designed PCB that implements a simple trans-impedance amplifier in a convenient physical package, providing a bandwidth (BW) between XXX and XXX, depending on the transimpedance gain, which can be set by a resistor. 
The photodiode can be safely operated up to incident powers of approximately 10 mW, which sets a XXX dBc shot noise limit on the RIN that can be detected.
A photodiode with a BW of XXX MHz is used to characterize the system, while photodiodes with a bandwidth of XXX and correspondingly higher gain are used for feedback.

The chosen photodiode (Hamamatsu XXX) is an InGaS based, small-area, low-noise design with a high efficiency at 1064 nm.
Prior to use, the protective window is removed from the photodiode to prevent interference effects.
Further, to reduce the capacitance of the system, a reverse bias of XXX V is applied to the photodiode by a temperature-stabilized voltage reference (Digi-key XXX).
The transimpedance circuit is shown in figure XXX - it converts the photo-current supplied by the photodiode to a voltage signal using the low noise XXX operational amplifier. 
The electronic assembly is housed in a metal enclosure to minimize interference effects, but is mounted to the optical table using isolating mica posts, to prevent ground loops.

Light is focused onto the photodiode using a 25.4 mm lens such that the beam at the photodiode is significantly smaller than the photodiode diameter, to prevent pointing fluctuations from registering as positional fluctuations. 
An iris and interference filter (Semrock XXX) are used to elimnate stray sources of light.

FIGURE: Transimpedance amplifier, with our parameters
\begin{itemize}
	\item Transimpedance amplifier - typical parameters
	\item design criteria, part numbers, typical voltage levels
	\item cutting off windows
	\item thermal stuff (inGas)
	\item lens or no
	\item using photodiodes for looking at these thing
\end{itemize}

@@

Passive stability, while critical, has been found to be insufficient to ensure smoothe operation over many hours. Changes in weather conditions, load on the water-cooling systems and other external effects can lead to a slow drift in the pointing of the laser beams. 
To prevent external influences from contaminating large data sets, we have implemented an independent monitoring system to verify appropriate pointing of both lattice laser beams and eliminate experimental realizations when the system was in an undesired state.
This system is based on picking off a small portion of the beam shortly before it reaches the atomic system and imaging it onto a camera in the same plane as the atoms.

A limitation of this scheme is that the position of the atoms is dictated by the potential generated by the overlap of the ingoing and retro-reflected beams, while the monitoring camera only observes the position of the ingoing beam.
In order to verify that the monitor camera could be correlated with the true position of the atoms, purposeful misalignment of the incoming beams was introduced to the system, and the position of the atoms was compared to the monitor system reading, where the comparison is shown in figure XXX.
The position of the atoms was assumed to be related to the monitor camera by an affine transformation and a fit was performed, which implied that the monitor camera could predict the position of the atoms to within XX $\mu$m.

Further, Figure xxx shows the performance of the system in action during a long dataset, where the system performance was thought to have degraded due to environmental factors toward the end of the set.
